Comprehensive Quality-Aware Automated Semantic Web Service Composition

### 2017-01-26 paper.tex
update

\section{Related Work} \label{relatedWork}
\textbf{Semantic web service matchmaking}. Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused primarily on non-functional requirements consistently neglecting functional requirements. However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition. To the best of our knowledge, \cite{fanjiang2014semantic,lecue2009optimizing,pop2009immune} reported some recent attempts on service composition that considers both nonfunctional (QoS) and functional (semantic) aspects. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} to search for services that ensure semantic matching utilising an ontology of the corresponding domain.

@@

In this section, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS. PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2016particle}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional. Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache. In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights. Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect. \ref{pso_algorithm}, where the position is mapped to the index of service queue. later on, the updated service queue is used to decode a new weighted graph as the composition solution. Step 4. Lastly, the best position found in the searching space is selected and decode into the final optimised solution. This PSO-based approach is different from \cite{da2016particle}, as we use weighted graphs as solution presentation.
\subsection{Semantic Matchmaking} \label{semantic_matchmaking}
To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match demonstrated in Sect. \ref{semantic Web service Discovery}. The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$. Meanwhile, the quality of matched concepts are calculated in the quality model in subSection \ref{qualityModel}. The purpose of semantic matchmaking is to find more component services that could also potentially satisfy the quality of QoS with good functional quality.

@@

\subsection{Comprehensive Quality Model and Aggregation Matrix}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} that ignores quality of semantic matchmaking.

@@

First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}. The QoS-aware approach record $Q_{mt}$, $Q_{s}$ and utilise fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, in which $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach. We observe an interesting pattern from Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those by QoS-aware approach with one exception in Task 2 while the combination of mean $Q_{mt}$ and $Q_{s}$ at optimum in Task 2 is still significantly higher in our approach under statistical anlysis. Meanwhile, $Q_{QoS}$ generated by QoS-aware approach can obtain a slightly higher value than that of our approach. In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.
\begin{table}[]
\footnotesize
\centering
\caption{Mean Quality for comprehensive quality-aware methods and QoS-aware approach}
\label{decisionTable}
\begin{tabular}{l|l|l|l}
\hline
\multicolumn{2}{c|}{WSC09}              & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
\multirow{3}{*}{Task1}  &$Q_{mt}$   &0.189787 $\pm$ 0.039278686  &0.220594 $\pm$ 0.009318 $\uparrow$ \\ \cline{2-4} 
                        &$Q_{s}$    &0.884962 $\pm$ 0.014140   &0.893713 $\pm$ 0.007769  $\uparrow$ \\ \cline{2-4}
                        &$Q_{QoS}$  &0.278730 $\pm$ 0.007786     &0.279548 $\pm$ 0.007627                          \\ \hline
\multirow{3}{*}{Task2}  &$Q_{mt}$   &0.001795 $\pm$ 0.000719 $\uparrow$    &0.001135 $\pm$ 0.000633  \\ \cline{2-4} 
                        &$Q_{s}$    &0.906971 $\pm$ 0.005855     &0.927965 $\pm$ 0.007306 $\uparrow$   \\ \cline{2-4}
                        &$Q_{QoS}$  &0.239979 $\pm$ 0.000578 $\uparrow$     &0.237845 $\pm$ 0.001439 \\ \hline
\multirow{3}{*}{Task3}  &$Q_{mt}$   &0.158526 $\pm$ 0.014028               &  0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
                        &$Q_{s}$    &0.949109 $\pm$ 0.002331           &   0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
                        &$Q_{QoS}$  &0.247002 $\pm$ 0.000661 $\uparrow$             &  0.245631 $\pm$ 0.000431            \\ \hline
\multirow{3}{*}{Task4}  &$Q_{mt}$   &0.000000 $\pm$ 0.000000  &0.000001 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
                        &$Q_{s}$    &0.880058 $\pm$ 0.006603    &0.930632 $\pm$ 0.009043 $\uparrow$ \\ \cline{2-4}
                        &$Q_{QoS}$  &0.242338 $\pm$ 0.000516 $\uparrow$    &0.236677 $\pm$ 0.002211  \\ \hline
\multirow{3}{*}{Task5}  &$Q_{mt}$   &  0.000042 $\pm$ 0.000030     &  0.000078 $\pm$ 0.000031 $\uparrow$           \\ \cline{2-4} 
                        &$Q_{s}$    &  0.915933 $\pm$ 0.012888      &  0.928189 $\pm$ 0.002486 $\uparrow$                 \\ \cline{2-4}
                        &$Q_{QoS}$  & 0.238189 $\pm$ 0.000240$\uparrow$      &  0.237232 $\pm$  0.000391  \\ \hline                                                   
\end{tabular}
\end{table}

>>>>

\section{Related Work} \label{relatedWork}
\textbf{Semantic web service composition}. Substantial work \cite{bansal2016generalized,mier2015integrated,da2016particle,da2015graphevol,yu2013adaptive} on web service composition focused primarily on non-functional requirements consistently neglecting functional requirements. However few researchers addressed both functional and nonfunctional requirements at the same time in web service composition. To the best of our knowledge, \cite{lecue2009optimizing,fanjiang2014semantic,pop2009immune} reported some recent attempts on service composition that considers both nonfunctional (QoS) and functional (semantic) aspects. Semantic matchmaking utilises Description Logic($DL$) \cite{baader2003description} to search for services that ensure semantic matching utilising an ontology of the corresponding domain.

The combination of enhancing planning graph (EPG) and clonal selection algorithm is introduced in the work \cite{pop2009immune}  to solve web service optimisation problem as an immune-inspired web service composition approach. During the clonal selection process, the antigen is represented as a fitness function, and the antibody is represented as a binary alphabet to encode EPG. In this work,  semantic matchmaking is considered by measuring the quality of the similarity measure using information retrieval technique.

@@

In this section, we propose a comprehensive quality model for automated semantic service composition, and optimise both the quality of semantic matchmaking and QoS. PSO has shown its efficiency in solving combinatorial optimisation problems \cite{fukuyama2008fundamentals}. Therefore, we will employ a PSO-based approach, which is considered to be simple and efficient without penalising or repairing that often required by GP \cite{da2016particle}. Fig. \ref{overview} shows the overview of our approach with five steps. Step 1: The composite process is triggered by a composite goal defined in Subsection \ref{problemDes}, which describes customers requirements both functional and non-functional. Step 2: This composition goal are used to discover all relevant web services, which lead to a shrunken service repository that is subsequently used by PSO as a searching space. Step 3: A weighted graph representation is randomly built up from the an initial service queue that mapped to the particle's location, interleaving with semantic matchmaking process utilising ontology-based index cache. In the weighted graph, graph edges are assigned with semantic matchmaking quality as weights. Step 4: The fitness value of the weighted graph is evaluated to update the position of particle under PSO algorithm in Sect. \ref{pso_algorithm}, where the position is mapped to the index of service queue. later on, the updated service queue is used to decode a new weighted graph as the composition solution. Step 4. Lastly, the best position found in the searching space is selected and decode into the final optimised solution. This PSO-based approach is different from \cite{da2016particle}, as we use weighted graphs as solution presentation.

\subsection{Semantic Matchmaking} \label{semantic_matchmaking}
To perform semantic matchmaking, we transfer a function match between $S_{1}: S_{output} \in C_{1}$ and $S_{2}:S_{output} \in S_{b}$ to a pair of concept match demonstrated in Sect. \ref{semantic Web service Discovery}. The matching process attempts to determine semantic matching between the source concepts of $C_{1}$ and the target concepts of $C_{2}$. Meanwhile, the quality of matched concepts are calculated in the quality model in subSection \ref{qualityModel}. The purpose of semantic matchmaking is to find more component services that could also potentially satisfy the quality of QoS with good functional quality.

@@

\subsection{Comprehensive Quality Model and Aggregation Matrix}\label{qualityModel}
In this paper, we propose a comprehensive quality model to evaluate the overall quality of semantic web service composition. This model overcome the disadvantages of current prevailing QoS-aware optimisation that ignores quality of semantic matchmaking.

@@

First, we look at mean value of $Q_{mt}$, $Q_{s}$ and $Q_{QoS}$ at optimum at the 100th generation for two approaches, shown in Table \ref{decisionTable}. The QoS-aware approach record $Q_{mt}$, $Q_{s}$ and utilise fitness function $Fitness = w_1 \hat{A} + w_2 \hat{R} + w_3(1 - \hat{T}) + w_4(1 - \hat{C})$ when $\sum_{i=1}^{4} w_i = 1$ without considering $MT$ and $S$, in which $Q_(QoS)$ is normalised from 0 to 0.5 to make it comparable to $Q_{QoS}$ in our approach. We observe an interesting pattern from Table \ref{decisionTable} using statistic analysis: mean value of $Q_{mt}$ and $Q_{s}$ at optimum by our approach is consistently higher than those by QoS-aware approach.  Meanwhile, $Q_{QoS}$ generated by QoS-aware approach can obtain a slightly higher value than that of our approach. In conclusion, we can perceive that our evaluation could find out better functional quality with a reasonable trade off in QoS.
\begin{table}[]
\footnotesize
\centering
\caption{Mean Quality for comprehensive quality-aware methods and QoS-aware approach}
\label{decisionTable}
\begin{tabular}{l|l|l|l}
\hline
\multicolumn{2}{c|}{WSC09}              & \shortstack{QoS-aware \\ Evaluation} & \shortstack{Comprehensive \\ Quality Evaluation} \\ \hline
\multirow{3}{*}{Task1}  &$Q_{mt}$   &0.189787 $\pm$ 0.039278686            &0.221862 $\pm$ 0.009582 $\uparrow$ \\ \cline{2-4} 
                        &$Q_{s}$    &0.884962 $\pm$ 0.014140               &0.894082 $\pm$ 0.009206 $\uparrow$ \\ \cline{2-4}
                        &$Q_{QoS}$  &0.278730 $\pm$ 0.007786               &0.280222 $\pm$ 0.008212                          \\ \hline
\multirow{3}{*}{Task2}  &$Q_{mt}$   &0.001795 $\pm$ 0.000719               &0.001977 $\pm$ 0.001566 $\uparrow$ \\ \cline{2-4} 
                        &$Q_{s}$    &0.906971 $\pm$ 0.005855               &0.923970 $\pm$ 0.006898 $\uparrow$   \\ \cline{2-4}
                        &$Q_{QoS}$  &0.239979 $\pm$ 0.000578 $\uparrow$    &0.238596 $\pm$ 0.001264 \\ \hline
\multirow{3}{*}{Task3}  &$Q_{mt}$   &0.158526 $\pm$ 0.014028               &0.245830 $\pm$ 0.007761 $\uparrow$   \\ \cline{2-4} 
                        &$Q_{s}$    &0.949109 $\pm$ 0.002331               &0.972765 $\pm$ 0.002980 $\uparrow$           \\ \cline{2-4}
                        &$Q_{QoS}$  &0.247002 $\pm$ 0.000661 $\uparrow$    &0.245631 $\pm$ 0.000431            \\ \hline
\multirow{3}{*}{Task4}  &$Q_{mt}$   &0.000000 $\pm$ 0.000000               &0.000004 $\pm$ 0.000002 $\uparrow$ \\ \cline{2-4} 
                        &$Q_{s}$    &0.879514 $\pm$ 0.007456               &0.920733 $\pm$ 0.000001 $\uparrow$ \\ \cline{2-4}
                        &$Q_{QoS}$  &0.242297 $\pm$ 0.000507 $\uparrow$    &0.236677 $\pm$ 0.002211  \\ \hline
\multirow{3}{*}{Task5}  &$Q_{mt}$   &  0.000042 $\pm$ 0.000030             &0.000078 $\pm$ 0.000020 $\uparrow$           \\ \cline{2-4} 
                        &$Q_{s}$    &  0.915933 $\pm$ 0.012888             &0.927678 $\pm$ 0.002578 $\uparrow$                 \\ \cline{2-4}
                        &$Q_{QoS}$  & 0.238189 $\pm$ 0.000240 $\uparrow$      &  0.237485 $\pm$  0.000328  \\ \hline                                                   
\end{tabular}
\end{table}
